---
title: "R Notebook"
output: 
 html_document:
  toc: true
  theme: simplex
  highlight: kate
  code_folding: show 
---


```{r, warning=FALSE, message=FALSE}

library(tidyverse)
library(scales)

```

### Load the data
```{r, warning=FALSE, message=FALSE}

data.raw <- read_csv("Looks_v_Personality.csv")

```

### Process the data
```{r}

data.prep <- data.raw %>% 
  # Exclude the unweighted sample - non representative of the population
  # Exclude the text description of rank
  select(-unweighted_sample, -rank_text) %>% 
  mutate(nationality = factor(nationality)
         , gender = factor(gender, levels = c("Men", "Women"), labels = c("M", "F"))
         #, rank_num = factor(rank_num, levels = c(6:1), labels = c(6:1), ordered = T)
         , value_pc = if_else(gender == "M", -value_pc, value_pc))

```

### Understand the data
```{r}

# Print a list of countries
data.prep %>% 
  select(nationality) %>% 
  distinct()

# Extract a sample of the primary key fields
data.prep %>% 
  filter(gender == "M" & nationality == "French") %>% 
  select(nationality, gender, question) %>% 
  distinct()

```

### Prepare data for visualisation
```{r}

offset.cntry <- 0.100
offset.world <- 0.200

func_chooseNationality <- function(inputNationality) {
  
  data.plot <- data.prep %>% 
    filter(nationality == inputNationality) %>%  
    mutate(rank_num = rank_num - offset.cntry)

  # Prepare an object for the rest of the world
  data.world <- data.prep %>% 
    # Exclude the chosen country from this object
    filter(nationality != inputNationality) %>% 
    mutate(rank_num = rank_num + offset.world)
  
  rtn.list <- list(cntry = data.plot, world = data.world)
  
  return(rtn.list)
  
}

plot.Australian <- func_chooseNationality("Australian")
plot.British <- func_chooseNationality("British")
plot.HongKong <- func_chooseNationality("Hong Kong")

```


### Visualise the data {.tabset .tabset-fade .tabset-pills}
Begin by preparing a theme object
```{r }

ggtheme <- theme(axis.title = element_text(size = 8, colour = "grey60")
                 , axis.text = element_text(size = 6, colour = "grey60")
                 , axis.line = element_line(colour = "grey90")
                 , axis.ticks = element_blank()
                 , panel.background = element_blank()
                 , panel.border = element_blank()
                 , panel.grid.major = element_blank()
                 , panel.grid.minor = element_blank()
                 , legend.background = element_blank()
                 , legend.box.background = element_blank()
                 , legend.title = element_text(size = 8, colour = "grey60")
                 , legend.text = element_text(size = 7, colour = "grey60")
                 , legend.key = element_rect(fill = NA)
                 , plot.subtitle = element_text(size = 8, colour = "grey40")
                 , plot.title = element_text(size = 12, colour = "grey40")
                 , strip.background = element_blank()
                 , strip.text = element_text(size = 8, colour = "grey60"))

```

Create a function for repeated plotting. The function receives two datasets:  
  
  + Country specific dataset  
  + Rest of the world dataset
```{r }

func_plotCountry <- function(inputCountry, inputWorld) {
  
  # Extract the country name for the plot title
  lbl <- inputCountry %>% 
    select(nationality) %>% 
    mutate(nationality = as.character(nationality)) %>% 
    distinct() %>% 
    as.character()
  
  g <- ggplot() +
    # Add the first layer of points for the country
    # Using ticks to represent their values
    # Colour by gender
    geom_point(data = inputCountry
             , aes(y = rank_num, x = value_pc, colour = gender)
             , alpha = 1, shape = "|", size = 3) +
    # Add the next layer of points for the rest of the world
    # Using the same gender attribute for colour and fill
    geom_point(data = inputWorld
               , aes(y = rank_num, x = value_pc, colour = gender, fill = gender)
               , alpha = 0.05, shape = 22, size = 2.25) +
    # Add a layer of labels for this particular country
    geom_text(data = inputCountry %>% filter(abs(value_pc) > 0.05)
             , aes(y = rank_num - 0.35, x = value_pc, colour = gender, label = scales::percent(abs(value_pc)))
             , alpha = 1, size = 2.75, show.legend = F) +
    ggtheme + 
    # Assign colour and fill scales
    scale_fill_manual(values = c("M" = "dodgerblue2", "F" = "firebrick2")) +
    scale_colour_manual(values = c("M" = "dodgerblue3", "F" = "firebrick3")) +
    # Force the x axis to show an absolute value
    scale_x_continuous(labels = scales::trans_format("abs", percent)) + 
    # Reverse the direction of the y axis so the ordering is intuitive
    scale_y_reverse(breaks = c(1:6)) + 
    #scale_y_continuous() +
    ylab("Rank (Importance)") + 
    xlab("% of respondants") +
    # Create panels for each question
    facet_wrap(~question) +
    # Add a plot title
    ggtitle(paste0("Ranked measures of compatability for ", lbl, " men and women")
            , subtitle = paste0("Ticks showing results for the ", lbl
            , " population, compared to rest of the world distribution"))
  
  return(g)
  
}

```

#### Britain
```{r fig.width=9, fig.height=6}

func_plotCountry(inputCountry = plot.British$cntry
                 , inputWorld = plot.British$world)

```
  
Some observations about the British:  
  
  + Money doesn't really matter for the Brits. The majority of respondants gave this the lowest, and mostly out-scoring the rest of the world for both genders.  
  + Looks also don't matter a lot. The distribution for British men however, was more skewed towards looks making mattering compared to women.   
  + Similar interests however, are pereived as more important for women than men.  
  
***
#### Hong Kong
```{r fig.width=9, fig.height=6}

func_plotCountry(inputCountry = plot.HongKong$cntry
                 , inputWorld = plot.HongKong$world)


```
  
Some observations on people in Hong Kong: 
  
  + Money doesn't matter much for both men and women. Compared to the rest of the world however, money mattered just a little bit more.
  + For men, looks are quite important compared to the rest of the world. 
  + Personality is still important, but not as important as rated by the most of the rest of the world. 
  
***
#### Australia
```{r fig.width=9, fig.height=6}

func_plotCountry(inputCountry = plot.Australian$cntry
                 , inputWorld = plot.Australian$world)

```
  
Some observations about Australians:  
  
  + In terms of importance of money and personality, Australian men and women sit mid-field among other coutries. 
  + Across the other measures, Australians are also placed roughly in the middle of the distribution. Perhaps this is a testament to the multicultural composition of Australian society.  
  

***
### Conclusions  
Generally across the world, money doesn't matter as much as personality does. Comforting, I guess. 